---
title: "p8105_hw6_ph2538"
author: "Pei Yang Hsieh"
date: 2018-11-18
output: github_document
---


```{r setup, include=FALSE}
library(tidyverse)
library(modelr)
library(mgcv)
```

## Problem 1

### Tidying Data

Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. Modifiy victim_race to have categories white and non-white, with white as the reference category. Be sure that victim_age is numeric.

```{r}
homicide_data = read_csv(file = "./homicide-data.csv")

#create city_state variable and omit certain cities
homicide_data =
  homicide_data %>% 
  mutate(city_state = str_c(city, ", ", state)) %>% 
  filter(city_state != "Dallas, TX", city_state != "Phoenix, AZ", city_state != "Kansas City, MO", city_state != "Tulsa, AL") 

#create binary variable
homicide_data = 
  homicide_data %>% 
  mutate(hom_solved = recode(disposition, "Closed by arrest" = "Yes", "Closed without arrest" = "No", "Open/No arrest" = "No")) %>%
  mutate(hom_solved = as.factor(hom_solved))

#modify victim_race to binary category. Note that "Unknown" race is included in Non-white category.
homicide_data = 
  homicide_data %>% 
  mutate(victim_race = recode(victim_race, 'White' = "White", 'Hispanic' = "Non_white", 'Other' = "Non_white", 'Black' = "Non_white", 'Asian' = "Non_white", 'Unknown' = "Non_white")) %>% 
  mutate(victim_race = fct_relevel(victim_race, "White"))

#change victim_age to numeric
homicide_data = 
  homicide_data %>% 
  mutate(victim_age = as.numeric(victim_age))


```



### GLM on Baltimore, MD

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing nonwhite victims to white victims keeping all other variables fixed.

```{r}
Baltimore_df = 
  homicide_data %>% 
  filter(city_state == "Baltimore, MD") %>% 
  select(hom_solved, victim_age, victim_race, victim_sex)

Baltimore_glm = 
  Baltimore_df %>% 
  glm(hom_solved ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate)) %>%
  mutate(conf.low = exp(estimate - (1.96 * std.error)), 
         conf.high = exp(estimate + (1.96 * std.error))) %>% 
  select(term, log_OR = estimate, OR, p.value, conf.low, conf.high) %>% 
  filter(term == "victim_raceNon_white") %>% 
  knitr::kable(digits = 3)

Baltimore_glm  
  
```


The adjusted OR for solving homicides comparing nonwhite victims to white victims is 0.441.

### GLM on all cities

Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing nonwhite victims to white victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.

```{r}

all_cities_df = 
  homicide_data %>% 
  select(city_state, hom_solved, victim_age, victim_race, victim_sex)

all_cities_glm = 
  all_cities_df %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(model = map(data, ~glm(hom_solved ~ victim_age + victim_race + victim_sex, data = ., family = binomial())),
  model = map(model, broom::tidy)) %>% 
  select(-data) %>% 
  unnest() %>% 
  mutate(OR = exp(estimate)) %>%
  mutate(conf.low = exp(estimate - (1.96 * std.error)), 
         conf.high = exp(estimate + (1.96 * std.error))) %>% 
  select(city_state, term, log_OR = estimate, OR, p.value, conf.low, conf.high) %>% 
  filter(term == "victim_raceNon_white")

all_cities_glm

```


### Plot estimates and CIs on all cities

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

```{r, eval = FALSE}
Plot_all_cities =
  all_cities_glm %>% 
  ggplot(aes(fct_reorder(city_state, OR), OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  labs(
    title = "Estimates and CIs for All Cities",
    x = "City",
    y = "Estimates"
  )  +
  theme(axis.text.x = element_text(angle = 90)) 

Plot_all_cities
```



## Problem 2

Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

```{r}
birthweight_data = read_csv(file = "./birthweight.csv")

birthweight_data = 
  birthweight_data %>%
  mutate(babysex = as.factor(babysex), frace = as.factor(frace), malform = as.factor(malform), 
         mrace = as.factor(mrace))
```

### Build a model

Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

```{r}
mod_inc_mrace = 
  birthweight_data %>%
  select(bwt, fincome, mrace)

lm_inc_mrace = lm(bwt ~ fincome + mrace, mod_inc_mrace)

lm_inc_mrace %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

modelr::add_residuals(mod_inc_mrace, lm_inc_mrace)

modelr::add_predictions(mod_inc_mrace, lm_inc_mrace)
  
```

### Plot model

```{r}
mod_inc_mrace %>% 
  modelr::add_residuals(lm_inc_mrace) %>% 
  ggplot(aes(x = mrace, y = resid)) + geom_violin()
```


```{r}
mod_inc_mrace %>% 
  modelr::add_predictions(lm_inc_mrace) %>% 
  ggplot(aes(x = mrace, y = pred)) + geom_violin()
```


### Creating 2 other models

Compare your model to two others:
One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

```{r}
mod_len_age = 
  birthweight_data %>%
  select(bwt, blength, gaweeks)

lm_len_age = lm(bwt ~ blength + gaweeks, mod_len_age)

lm_len_age %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

modelr::add_residuals(mod_len_age, lm_len_age)

modelr::add_predictions(mod_len_age, lm_len_age)
```



```{r}
mod_hc_len_sex = 
  birthweight_data %>%
  select(bwt, bhead, blength, babysex)

lm_hc_len_sex = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, mod_hc_len_sex)

lm_hc_len_sex %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

modelr::add_residuals(mod_hc_len_sex, lm_hc_len_sex)

modelr::add_predictions(mod_hc_len_sex, lm_hc_len_sex)
```

## Comparing 3 models

```{r}
cv_df = 
  crossv_mc(birthweight_data, 100) 

# cv_df %>% pull(train) %>% .[[1]] %>% as_tibble
# 
# cv_df %>% pull(test) %>% .[[1]] %>% as_tibble
# 
# cv_df =
#   cv_df %>% 
#   mutate(train = map(train, as_tibble),
#          test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(mod_inc_mrace = map(train, ~lm(bwt ~ fincome + mrace, data = .x)),
         mod_len_age = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         mod_hc_len_sex = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = .x))) %>% 
  mutate(rmse_inc_mrace    = map2_dbl(mod_inc_mrace, test, ~rmse(model = .x, data = .y)),
         rmse_len_age = map2_dbl(mod_len_age, test, ~rmse(model = .x, data = .y)),
         rmse_hc_len_sex = map2_dbl(mod_hc_len_sex, test, ~rmse(model = .x, data = .y)))

```


## Plot RMSE

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "rmse_", ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```


```{r}
rmse(lm_inc_mrace, birthweight_data)

rmse(lm_len_age, birthweight_data)

rmse(lm_hc_len_sex, birthweight_data)
```


The hc_len_sex model is the best because it has the lowest RMSE value of `r rmse(lm_hc_len_sex, birthweight_data)`. 
