---
title: "p8105_hw6_ph2538"
author: "Pei Yang Hsieh"
date: 2018-11-18
output: github_document
---


```{r setup, include=FALSE}
library(tidyverse)
```

## Problem 1

Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. Modifiy victim_race to have categories white and non-white, with white as the reference category. Be sure that victim_age is numeric.

```{r}
homicide_data = read_csv(file = "./homicide-data.csv")

#create city_state variable and omit certain cities
homicide_data =
  homicide_data %>% 
  mutate(city_state = str_c(city, ", ", state)) %>% 
  filter(city_state != "Dallas, TX", city_state != "Phoenix, AZ", city_state != "Kansas City, MO", city_state != "Tulsa, AL") 

#create binary variable
homicide_data = 
  homicide_data %>% 
  mutate(hom_solved = disposition != "Closed without arrest" & disposition != "Open/No arrest")

#modify victim_race to binary category
homicide_data = 
  homicide_data %>% 
  mutate(victim_race = recode(victim_race, 'White' = "White", 'Hispanic' = "Non_white", 'Other' = "Non_white", 'Black' = "Non_white", 'Asian' = "Non_white", 'Unknown' = "Non_white"))

#change victim_age to numeric
homicide_data = 
  homicide_data %>% 
  mutate(victim_age = as.numeric(victim_age))


```

